HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex

In order to validate the HUME metric, we ran an annotation experiment with one source language (English), and four 
target languages (Czech, German, Polish and Romanian), using text from the public health domain. We are 
particularly interested in this domain since our ultimate goal is to provide high-quality translations of health
information for speakers of languages other than English, and in this domain accurate transfer of meaning is
paramount.

Our annotation experiment sought to address the following questions:
\begin{compactitem}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{compactitem}

\subsection{UCCA Annotation}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists\oa{were there no other annotators from Prague? Ondrej
does not remember! Was it just Ondrej+Jana Sindlerova? Then it would be one
computer scientist and one linguist for Czech.}.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair.

>>>>

In order to validate the HUME metric, we ran an annotation experiment with one source language (English), and four 
target languages (Czech, German, Polish and Romanian), using text from the public health domain.
The domain is particularly suitable for experimenting on MT evaluation, as being able to determine
whether the translation accurately conveys the same information as the source is here paramount.

%particularly interested in this domain since our ultimate goal is to provide high-quality translations of health
%information for speakers of languages other than English, and in this domain accurate transfer of meaning is
%paramount.

The experiment seeks to address two questions:

\begin{compactitem}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{compactitem}

\subsection{UCCA Annotation}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists and one linguist.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair\oa{I think we should probably
  say how many in each.}.
